Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-06-16 ms.tex
Update on Overleaf.

Converting polarised beamformed voltages on the sky to Stokes intensities and temporally averaging them as per Equation~(\ref{eqn:opt-pol-corr-img-outprod}) requires $n_\textrm{p}^2$ complex "squaring" (complex products) and subsequent complex additions for each of the complex polarised voltage beams, and therefore $n_\textrm{p}^2 n_\textrm{bs}$ CMACs per station channel, amounting to $8 n_\textrm{p}^2 n_\textrm{bs}$ FLOPS per station per channel. Hence, the net rate corresponding to beamforming, squaring, and averaging is $8 n_\textrm{p}^2 (D_\textrm{s}/D_\textrm{a})^2 (N_\textrm{a/s}+1)/\delta t$ FLOPS per station per channel.

@@

Figure~\ref{fig:multidim-incoherent-compcost-BF-LAMBDA-I} shows the covariance of the total computational cost density per station per voxel for the beamforming architecture taken two station parameters at a time while keeping the rest fixed at the nominal values of a \texttt{LAMBDA-I} station denoted by grey dashed lines. The variation in the cost per voxel is dominated by the beamforming cost and displays the same trends observed in Figure~\ref{fig:1D-incoherent-compcost-BF-LAMBDA-I}, namely, linear in $N_\textrm{a/s}$ while remaining constant with $D_\textrm{a}$ and $D_\textrm{s}$.

@@

% \appendix

>>>>

Converting polarised beamformed voltages on the sky to Stokes intensities and temporally averaging them as per Equation~(\ref{eqn:intra-station-opt-pol-img-outprod}) requires $n_\textrm{p}^2$ complex "squaring" (complex products) and subsequent complex additions for each of the complex polarised intesity beams, and therefore $n_\textrm{p}^2 n_\textrm{bs}$ CMACs per station channel, amounting to $8 n_\textrm{p}^2 n_\textrm{bs}$ FLOPS per station per channel. 
% Hence, the net rate corresponding to beamforming, squaring, and averaging is $8 n_\textrm{p}^2 (D_\textrm{s}/D_\textrm{a})^2 (N_\textrm{a/s}+1)/\delta t$ FLOPS per station per channel.

@@

Figure~\ref{fig:multidim-incoherent-compcost-BF-LAMBDA-I} shows a covariant view of the total computational cost density per station per voxel for the beamforming architecture taken two station parameters at a time while keeping the rest fixed at the nominal values of a \texttt{LAMBDA-I} station denoted by grey dashed lines. The variation in the cost per voxel is dominated by the beamforming cost and displays the same trends observed in Figure~\ref{fig:1D-incoherent-compcost-BF-LAMBDA-I}, namely, linear in $N_\textrm{a/s}$ while remaining constant with $D_\textrm{a}$ and $D_\textrm{s}$.

@@

\appendix
